Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-04 apples_and_oranges.qmd
A few notes

NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: In progress.
NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect. In the beginning of the results below, I explain in detail what is missing where. **CB**: I've checked and there are fewer psy active conditions that I expected - it seems some of the trials with multiple active arms have been filtered out. Also, for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data. The numbers look right for med studies.

>>>>

NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: Done.
NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect. In the beginning of the results below, I explain in detail what is missing where. **CB**: I've checked and there are fewer psy active conditions that I expected - it seems some of the trials with multiple active arms have been filtered out. I have now fixed this and the numbers look correct. The numbers look right for med studies. One thing - for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
